---
title: "Data Dive - Accountability Council: Draft Findings"
author: "Data Kind"
date: "6/23/2018"
output:
  html_document:
    toc: true
    toc-_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE)
library(here)
library(knitr)
library(printr)
library(kableExtra)
library(janitor)
library(tidyverse)
library(gridExtra)
library(cowplot)
library(ggpubr)
```

### Summary

IAMs which do NOT allow claimants to see or comment on draft findings have higher completion rates, while eligibility rates are are not consistent. All IAMs allow managmenet to see and comment draft findings, 

<!-- # Load data  -->
```{r}
load(here("/Raw/benchmark_data_cleaned.Rdata")) # benchmarks_cleaned
load(here("/Raw/benchmark_data_cleaned_melted.Rdata")) # benchmarks_melted
load(here("/Raw/accountability_console_data_cleaned.Rdata")) # complaints

dat_bench_wide <- benchmarks_cleaned
dat_bench_long <- benchmarks_melted
dat_compl <- complaints

# Summarize percent eligible by IAM 
dat_compl %>% 
  # Fix IAMs in dataset
  mutate(IAM = gsub("ABD_SPF_CRP","ADB_SPF_CRP",IAM),
         IAM = gsub("ERBD_PCM","EBRD_PCM",IAM),
         IAM = gsub("ERBD_IRM","EBRD_PCM",IAM),
 # Define completed process, among those outcome
         Status_complete = case_when(Status %in% c("Closed With Results","Monitoring") ~ "completed",
                                     Status %in% c("Closed Without Results") ~ "not completed")) %>% 
  group_by(IAM) %>% 
  summarise(elig_pct =  mean(ELIGIBLE,na.rm = T),
            elig_n = sum(!is.na(ELIGIBLE)),
            compltd_pct =  mean(Status_complete == "completed",na.rm = T),
            compltd_n = sum(!is.na(Status_complete))) %>% 
  select(IAM, elig_pct,elig_n,compltd_pct,compltd_n) %>% 
  arrange(desc(elig_pct)) ->
  dat_eligByIAM
```

<!-- Format further -->
```{r}
dat_bench_long %>% 
  rename(IAM = variable) %>% 
  # Add eligibility sumary
  left_join(dat_eligByIAM) %>% 
  mutate(IAM = fct_reorder(IAM,elig_pct,desc=T)) %>% 
  mutate(IAM_order = as.numeric(IAM),
         # Reduce wordiness of the benchmarks
        Benchmark = gsub("the mechanism","it",Benchmark),
        Benchmark = gsub("management","mgmt",Benchmark),
        Benchmark = gsub("recommendations","recom",Benchmark),
        Benchmark = gsub("available","avail",Benchmark),
        Benchmark = trimws(Benchmark),
        # Variable
        value = gsub("1","Yes",gsub("0","No",value)),
        value_40c = str_trunc(value,40),
        value = fct_relevel(factor(value),"Yes","No"),
        value_40c = fct_relevel(factor(value_40c),"Yes","No")) ->
  dat_bench_long
```

### Are draft findings made available to claimant?
```{r}
Category_here = "Compliance review findings or recommendations"
benchmark_here = grep("draft findings",unique(dat_bench_long$Benchmark),value=T)[1]
```

```{r makePlot_byElig, fig.width=8,fig.height=5}
dat_bench_long %>% 
  filter(Category == Category_here & Benchmark == benchmark_here) %>% 
  mutate(value_40c = fct_drop(value_40c)) ->
  dat_here

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}
cols = gg_color_hue(length(levels(dat_here$value_40c)))

cols[rev(levels(dat_here$value_40c))=="Yes"] = "#006400"
cols[rev(levels(dat_here$value_40c))=="No"] = "#D80000"


dat_here %>% 
  ggplot(aes(y=fct_rev(value_40c),x=elig_pct)) +
  geom_text(angle=45,aes(label=IAM, col=IAM,size=elig_n)) +
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10)) + 
  xlim(0,1) +
  labs(title = str_wrap(benchmark_here,70), subtitle="Individual IAM",y="",x="% Eligible",size="N") +
  guides(col=FALSE,fill=F)  ->
  plot_bar

dat_here %>% 
  ggplot(aes(fct_rev(value_40c))) +
  geom_bar(aes(fill=fct_rev(value_40c))) +
  coord_flip() +
  labs(y="",x="") +
  guides(fill=F) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  scale_fill_manual(values=cols) +
  scale_y_continuous(breaks=c(2,4,6,8),limits=c(0,10)) +
  labs(title="",subtitle="Frequency") ->
  plot_hist

arrangeGrob(plot_bar,plot_hist,                             
             ncol = 2, nrow = 1, 
             layout_matrix = rbind(c(1,1,1,1,2))) %>% 
  as_ggplot

# dat_compl %>% 
#   count(ELIGIBLE, Status)
```


```{r makePlot_byRslt, fig.width=8,fig.height=5}
dat_bench_long %>% 
  filter(Category == Category_here & Benchmark == benchmark_here) %>% 
  mutate(value_40c = fct_drop(value_40c)) ->
  dat_here

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}
cols = gg_color_hue(length(levels(dat_here$value_40c)))

cols[rev(levels(dat_here$value_40c))=="Yes"] = "#006400"
cols[rev(levels(dat_here$value_40c))=="No"] = "#D80000"


dat_here %>% 
  ggplot(aes(y=fct_rev(value_40c),x=compltd_pct)) +
  geom_text(angle=45,aes(label=IAM, col=IAM,size=compltd_n)) +
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10)) + 
  xlim(0,.5) +
  labs(title = str_wrap(benchmark_here,70), subtitle="Individual IAM",y="",x="% Completed",size="N") +
  guides(col=FALSE,fill=F)  ->
  plot_bar

dat_here %>% 
  ggplot(aes(fct_rev(value_40c))) +
  geom_bar(aes(fill=fct_rev(value_40c))) +
  coord_flip() +
  labs(y="",x="") +
  guides(fill=F) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  scale_fill_manual(values=cols) +
  scale_y_continuous(breaks=c(2,4,6,8),limits=c(0,10)) +
  labs(title="",subtitle="Frequency") ->
  plot_hist

arrangeGrob(plot_bar,plot_hist,                             
             ncol = 2, nrow = 1, 
             layout_matrix = rbind(c(1,1,1,1,2))) %>% 
  as_ggplot

# dat_compl %>% 
#   count(ELIGIBLE, Status)
```

### May claimants make comments on draft findings?
```{r}
benchmark_here = grep("draft findings",unique(dat_bench_long$Benchmark),value=T)[3]
```

```{r ref.label="makePlot_byElig", fig.width=8,fig.height=5}
```

```{r ref.label="makePlot_byRslt", fig.width=8,fig.height=5}
```

### Are claimants informed of draft findings before a report is made to the President / Board?
```{r}
benchmark_here = grep("draft findings",unique(dat_bench_long$Benchmark),value=T)[4]
```

```{r ref.label="makePlot_byElig", fig.width=8,fig.height=5}
```


```{r ref.label="makePlot_byRslt", fig.width=8,fig.height=5}
```


### Are draft findings made avail to mgmt?
```{r}
benchmark_here = grep("draft findings",unique(dat_bench_long$Benchmark),value=T)[2]
```

```{r ref.label="makePlot_byElig", fig.width=8,fig.height=5}
```

```{r ref.label="makePlot_byRslt", fig.width=8,fig.height=5}
```


### May mgmt make comments on draft findings?
```{r}
benchmark_here = grep("draft findings",unique(dat_bench_long$Benchmark),value=T)[5]
```

```{r ref.label="makePlot_byElig", fig.width=8,fig.height=5}
```

```{r ref.label="makePlot_byRslt", fig.width=8,fig.height=5}
```

